The Space of Feasible Execution Times for Asynchronous Periodic Task Systems using Definitive Idle Times

### 2013-07-31 dit-paper_ieee.tex
??? removed and task refactor
remarks of the last mail of LG

	Mathematically,
	\[
		\dbf{t_1, t_2} = \sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i
	\]
	where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
	and deadlines are both in the closed interval $[t_1, t_2]$.

@@

      The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility. They can all be written in the following way:
      \[
        \sum_{i=0}^{n-1} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
      \]
      Note that for a given $t$, we have that the $n_i(t)$ are
      constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

@@

  Even then, the number of constraints to consider is exponential in the number
  of tasks. While it has been shown that constraints that cover intervals ending
  after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
  therefore not usable for the purposes of this paper. The
  following concept is thus introduced, which is similar to the end of the busy period but does not depend on the execution times.

  \begin{definition}
    A \textbf{definitive idle time} (DIT) is a time $t$ such that every job
    released strictly before instant $t$ has its absolute deadline before or at instant $t$.
  \end{definition}

@@

		\[
			\sum_{i=0}^{n-1} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\]

@@

			For this reason, as shown by \cite{leung1982complexity}, it is sufficient (but pessimistic) to
			check for
			intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length
			in the number of tasks. A better interval is given in \cite{choquet2004minimal} using the
			notion of cyclic idle times (denoted $t_c$), which are dependent of the execution
			time and therefore cannot be used directly. The interval is $[0, t_c + H]$ and is valid for
			every $t_c$.

@@

For each $[a, d]$, we have a constraint $$\sum_{i=0}^{n-1} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.

>>>>

	Mathematically,
	\[
		\dbf{t_1, t_2} = \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i
	\]
	where $n_i(t_1, t_2)$ is the number of jobs of task $i$ which arrival times
	and deadlines are both in the closed interval $[t_1, t_2]$.

@@

      The DBF test gives us a list of inequations on the WCET values of the task set which together are a necessary and sufficient condition of feasibility. They can all be written in the following way:
      \[
        \sum_{i=1}^{n} n_i(t_1, t_2) \, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
      \]
      Note that for a given $t$, we have that the $n_i(t)$ are
      constant (w.r.t. the $C_i$). Those inequations are thus indeed linear.

@@

  Even then, the number of constraints to consider is exponential in the number
  of tasks. While it has been shown that constraints that cover intervals ending
  after the end of the first busy period are also redundant, this value depends on the $C_i$ and is
  therefore not usable for the purposes of this paper. The
  following concept, initially described by \cite{lipariaverage}, is thus introduced. It is similar to the end of the busy period but does not depend on the execution times.

  \begin{definition}
    A \textbf{definitive idle time} (DIT) \cite{lipariaverage} is a time $t$ such that every job
    released strictly before instant $t$ has its absolute deadline before or at instant $t$.
  \end{definition}

@@

		\[
			\sum_{i=1}^{n} n_i(t_1, t_2)
			\, C_i \leq t_2 - t_1 \; \forall \: 0 \leq t_1 \leq t_2
		\]

@@

			For this reason, as shown by \cite{leung1982complexity}, it is sufficient (but pessimistic) to
			check for
			intervals included in the interval $[O_{max}, O_{max} + 2H]$, which has an exponential length
			in the number of tasks. A better interval is given in \cite{choquet2004minimal} using the
			notion of cyclic idle times (denoted $t_c$), which are dependent of the execution
			time and therefore cannot be used directly. Their interval is $[0, t_c + H]$ and is valid for
			every cyclic idle time $t_c$.

@@

For each $[a, d]$, we have a constraint $$\sum_{i=1}^{n} n_i(a, d) \, C_i \leqslant d - a$$ which give a description of the C-space.
